Joint Power Allocation and Network Slicing In an End to End O-RAN System

### 2019-10-13 Latex/tex/pr.tex
add matlab code plot
add sth

their service requirements. Also RAN is decoupled to slices to provides services needs. Optimal power allocation and joint mapping slices to services is applied. In addition, mapping slices to physical resources is considered too.

@@

Furthermore, the mean arrival rate of second layer is approximately equal to the mean arrival rate of first layer $\alpha_{s} =\alpha_{s_1} \approx \alpha_{s_2}$ since, by using Burke’s Theorem, the arrival packets of second layer which is processed in first layer is still Poisson with rate $\alpha_{s}$  

@@

Also, in the Core Network (CN), there are $N_{D}$ data centers(DC), which served VNFs. Each DC contains several servers that supply VNF's needs.

@@

>>>>

their service requirements. Also RAN is decoupled to slices to provide services needs. Optimal power allocation and joint mapping slices to services is applied. In addition, mapping slices to physical resources is considered too.

@@

Furthermore, the mean arrival rate of second layer is approximately equal to the mean arrival rate of first layer $\alpha_{s} =\alpha_{s_1} \approx \alpha_{s_2}$ since, by using Burke’s Theorem, the arrival packets of second layer which is processed in first layer is still Poisson with rate $\alpha_{s}$. 

@@

Also, in the Core Network (CN), there are $D_c$ data centers (DC), which served VNFs. Each DC contains several servers that supply VNF's needs.

@@

\bibliographystyle{ieeetr}
\bibliography{ref}
